### 2016-07-20 doc/publications/plos16/plos16.tex
merge the R table into the main table

On the other hand, CursedForest (CF) is specifically designed to handle wide ``cursed" data. It avoids the correlation between
memory and dimensionality by not using Vectors. Data is instead stored in a columnar form in a Parquet format.

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Performance comparison between the different machine learning algorithms.}}
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
\bf{Genome \%}  & \bf{method} & \bf{Accuracy} & \bf{Runtime} & \bf{Memory/Node} \\
\hline
\multirow{3}{*}{8\% (chr1: 6,450,364)} & CursedForest & XX & 1hr 58min 23sec & 4GB \\
& RF (Spark ML) & 0.94 & 8hr 29min 07sec & 8GB \\
& LR &  & 10hr 30min & 8GB\\ \hline

\multirow{3}{*}{24\% (chr1-3: 19,328,051)}  & CursedForest & &  &\\
& RF(Spark ML) & &  &\\
& LR & &  &\\ \hline

\multirow{4}{*}{100\% (chr1-22: 81,047,467)} & CursedForest & 0.96 & 7hr 14min 40sec & 8GB \\ 
& RF (Spark ML) & - & - & - \\
& LR & - & - & - \\ 
& kmeans (Spark ML) & 0.82 & 30hr 44min 00sec & 24GB \\ \hline
\end{tabular}
\begin{flushleft} 
Comparison of different various machine learning libraries on different subsets of variant data 
from the 1000 Genomes Project.

@@

\begin{table}
\begin{minipage}{\textwidth}
\begin{center}
\begin{tabular}{|p{4.2cm}|l|l|l|l|l|l|l|}
\hline
\bf{method} & \bf{Accuracy} & \bf{Runtime} & \bf{Memory/Node} \\
\hline
RF (R)\footnote{10 nodes, 500 trees, dpas03} 
                                   &  0.456 & 2.89 & 18GB \\ \hline
CursedForest\footnote{something}
                                   & X & X & X \\ \hline
\end{tabular}
\medskip
\begin{flushleft} 
\caption{Comparion between Random Forests on R and CursedForests on a smaller
dataset. Chromosome 22 - phase1 (2.1GB) }
\label{table:smaller_data}
\end{flushleft}
\end{center}
%\end{sidewaystable}
\end{minipage}
\end{table}

>>>>

On the other hand, CursedForest (CF) is specifically designed to handle wide ``cursed" data. It avoids the relation between
memory and dimensionality, by not using Vectors. Instead, CursedForest stores data in the Parquet columnar format.

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Performance comparison between the different machine learning algorithms.}}
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
\bf{Genome \%}  & \bf{method} & \bf{Accuracy} & \bf{Runtime} & \bf{Memory/Node} \\
\hline

\multirow{3}{*}{phase1\_chr22: 1,092 x 490,036} & CursedForest &  &  &  \\
& RF (Spark ML) &  &  &  \\
& RF (R) & 0.456 & 2.89 & 18GB \\ \hline

\multirow{3}{*}{phase3\_chr1: 2,504 x 6,450,364} & CursedForest & XX & 1hr 58min 23sec & 4GB \\
& RF (Spark ML) & 0.94 & 8hr 29min 07sec & 8GB \\
& LR &  & 10hr 30min & 8GB\\ \hline

\multirow{3}{*}{phase3\_chr1-3: 2,504 x 19,328,051}  & CursedForest & &  &\\
& RF(Spark ML) & &  &\\
& LR & &  &\\ \hline

\multirow{4}{*}{phase3\_chr1-22: 2,504 x 81,047,467} & CursedForest & 0.96 & 7hr 14min 40sec & 8GB \\ 
& RF (Spark ML) & - & - & - \\
& LR & - & - & - \\ 
& kmeans (Spark ML) & 0.82 & 30hr 44min 00sec & 24GB \\ \hline
\end{tabular}
\begin{flushleft} 
Comparison of different various machine learning libraries on different subsets of variant data 
from the 1000 Genomes Project. Size of the data is individuals x variants

@@

%\begin{table}
%\begin{minipage}{\textwidth}
%\begin{center}
%\begin{tabular}{|p{4.2cm}|l|l|l|l|l|l|l|}
%\hline
%\bf{method} & \bf{Accuracy} & \bf{Runtime} & \bf{Memory/Node} \\
%\hline
%RF (R)\footnote{10 nodes, 500 trees, dpas03} 
 %                                  &  0.456 & 2.89 & 18GB \\ \hline
%CursedForest\footnote{something}
 %                                  & X & X & X \\ \hline
%\end{tabular}
%\medskip
%\begin{flushleft} 
%\caption{Comparion between Random Forests on R and CursedForests on a smaller
%dataset. Chromosome 22 - phase1 (2.1GB) }
%\label{table:smaller_data}
%\end{flushleft}
%\end{center}
%\end{sidewaystable}
%\end{minipage}
%\end{table}
